Visualizing the facebook friend's educational background using R
================================================================

Following the post by Romain Francois, Crawling facebook with R which provides a low-level interface to graph api of facebook. Using the concept, I tried to visualize the educational institutes that my friends were associated with. The method to access the access token from facebook is shown in Francois post.
Here is the code:

```{r}
#library used, RCurl, rjson, wordcloud

library(RCurl)
library(rjson)
library(wordcloud)

#function to access the facebook graph api

facebook <-  function( path = "me", access_token, options){
  if( !missing(options) ){
    options <- sprintf( "?%s", paste( names(options), "=", unlist(options), collapse = "&", sep = "" ) )
  } else {
    options <- ""
  }
  data <- getURL( sprintf( "https://graph.facebook.com/%s%s&access_token=%s", path, options, access_token ),ssl.verifypeer = FALSE )
  
  #convert json to R object
  fromJSON( data )
}
```

#Pass path and access key obtained from facebook graph API

```{r}
education <- facebook( path="me/friends.fields(education)" , access_token=access_token)
school<-education$friends$data[[1]]$education[[1]]$school$name[1]

#Extracting school names for each friend
for(i in 1:462){
  temp<-education$friends$data[[i]]$education[[1]]$school$name[1]
  if(is.null(temp))
    school[i]<-NA
  else{
  school[i]<-temp
  i<-i+1
  }
}

#Removing the NA

school<-school[!is.na(school)]


write.table(school, "c:/mydata.txt",row.names = FALSE, quote = FALSE)

schoolt<-table(school)

schooli<-subset(schoolt,schoolt>2)
}
```
#Creating the word cloud
wordcloud(names(schooli),log(as.numeric(schooli)),colors=c('red','green'))

This is an example of visualizing the data available from facebook. The final result is given below.
